---
title: "Chelan-Douglas-Okanogan Daily AQI Categories"
output:
  html_document: 
    css: report_styles.css
---

Processed on `r paste(lubridate::now(),format(lubridate::now(), "%Z"))`.

----

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE)

suppressPackageStartupMessages({
  library(AirMonitor)
})

```

# AQI Category-Days

The following tables summarize the number of days spent in each AQI category
during the July-October smoke season in each year. Tables include both
permanent and temporary monitors, many of which were deployed only briefly. 
The number of days with `Missing` values over each four month period is found in 
the rightmost column. 


```{r year_loop, results = "asis"}

# Define a function to convert numeric values into AQC categories
pm25_to_AQC <- function(x) {
  aqc <-
    cut(x, breaks = US_AQI$breaks_PM2.5, labels = US_AQI$names_eng)
  return(aqc)
}

baseUrl <- "http://smoke.mazamascience.com/Liz_Walker/CDHD_report/monitoring_data"

for ( year in 2014:2023 ) {
  
  startdate <- sprintf("%d0701", year)
  enddate <- sprintf("%d1101", year)
  timezone <- "America/Los_Angeles"
  
  dataReportUrl <- sprintf("%s/monitoring_data_%d.html", baseUrl, year)
  
  # ----- Assemble data --------------------------------------------------------
  
  # NOTE:  These paths are relative to the Rmd/ directory
  airnow <- get(load(sprintf("../data/airnow_%d.rda", year)))
  airsis <- get(load(sprintf("../data/airsis_%d.rda", year)))
  wrcc <- get(load(sprintf("../data/wrcc_%d.rda", year)))
  
  # NOTE:  We put airnow last so it's meta and data will be used  if an ID appears more than once
  monitor <-
    monitor_combine(
      wrcc, airsis, airnow,
      replaceMeta = TRUE,
      overlapStrategy = "replace all"
    ) %>%
    monitor_dropEmpty() %>%
    monitor_trimDate()
  
  cat("\n\n# `", year, "`\n")
  cat("\nIn the `", year, "` smoke season, `", nrow(monitor$meta), "` monitors were deployed.\n")
  cat("See the [data report](", dataReportUrl, ").\n")

  # ----- Create table ---------------------------------------------------------
  
  # Use cut() to convert PM2.5 measurements into Air Quality Category (AQC)
  dailyAQC <- 
    monitor %>%
    monitor_dailyStatistic(
      FUN = mean,
      na.rm = TRUE,
      minHours = 18,
      dayBoundary = c("LST")
    ) %>%
    monitor_dropEmpty() %>%
    monitor_mutate(
      FUN = pm25_to_AQC 
    )
  
  # Use base R (not dplyr) to assemble a table
  dayCounts <- data.frame(row.names = c(US_AQI$names_eng, "Missing"))
  for ( i in 2:ncol(dailyAQC$data) ) {
    # Site name
    siteName <- dailyAQC$meta$locationName[i-1]
    # AQC day counts
    aqcDayCounts <- 
      dplyr::pull(dailyAQC$data, i) %>%
      factor(levels = US_AQI$names_eng) %>%
      table(useNA = "always") %>%
      as.numeric()
    # Build up the table with one row per site
    dayCounts[[siteName]] = aqcDayCounts
  }
  
  categoryDaysBySite <- t(dayCounts)
  
  # ----- Print table ----------------------------------------------------------
  
  print(knitr::kable(categoryDaysBySite))
}
```


