---
title: "Chelan-Douglas-Okanogan Daily AQI Categories"
output:
  html_document: 
    css: report_styles.css
---

Processed on `r paste(lubridate::now(),format(lubridate::now(), "%Z"))`.

----

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE)

suppressPackageStartupMessages({
  library(AirMonitor)
})

```

_Disclaimer: Data presented here come from a variety of sources and do not 
represent official EPA measurements. Please visit
[AirNow](https://www.airnow.gov) for official measurements._

----

The following tables summarize the number of days each site spent in each AQI
category during the July-October smoke season in each year. Tables include both
permanent and temporary monitors, many of which were deployed only briefly. 
The number of days with `Missing` values over each four month period is found in 
the rightmost column. 


```{r year_loop, results = "asis"}

# # Define a function to convert numeric values into AQC categories
# pm25_to_AQC <- function(x) {
#   aqc <-
#     cut(x, breaks = US_AQI$breaks_PM2.5, labels = US_AQI$names_eng)
#   return(aqc)
# }
# 
# baseUrl <- "http://smoke.mazamascience.com/Liz_Walker/CDHD_report/monitoring_data"

baseUrl <- "."

for ( year in 2014:2023 ) {
  
  startdate <- sprintf("%d0701", year)
  enddate <- sprintf("%d1101", year)
  timezone <- "America/Los_Angeles"
  
  dataReportUrl <- sprintf("%s/monitoring_data_%d.html", baseUrl, year)
  
  # ----- Assemble data --------------------------------------------------------
  
  # NOTE:  These paths are relative to the Rmd/ directory
  airnow <- get(load(sprintf("../data/airnow_%d.rda", year)))
  airsis <- get(load(sprintf("../data/airsis_%d.rda", year)))
  wrcc <- get(load(sprintf("../data/wrcc_%d.rda", year)))
  
  # NOTE:  We put airnow last so it's meta and data will be used if an ID appears more than once
  monitor <-
    monitor_combine(
      wrcc, airsis, airnow,
      replaceMeta = TRUE,
      overlapStrategy = "replace all"
    ) %>%
    monitor_dropEmpty() %>%
    monitor_trimDate() %>%
    monitor_arrange(locationName)
  
  cat("\n\n# ", year, "\n")
  cat("\nIn the ", year, " smoke season, ", nrow(monitor$meta), " monitors were deployed.\n")
  cat("Please see the [data report](", dataReportUrl, ") to review input data.\n")

  # ----- Create table ---------------------------------------------------------
  
  dailyAQCTable <-
    monitor %>%
    monitor_dailyStatistic(
      FUN = mean,
      na.rm = TRUE,
      minHours = 18,
      dayBoundary = c("LST")
    ) %>%
    monitor_dropEmpty() %>%
    monitor_toAQCTable(NAAQS = "PM2.5")
  
  # ----- Print table ----------------------------------------------------------
  
  print(knitr::kable(dailyAQCTable))
}
```


