---
title: "Chelan-Douglas-Okanogan Monitoring Data"
output:
  html_document: 
    css: report_styles.css
---

Processed on `r paste(lubridate::now(),format(lubridate::now(), "%Z"))`.

----

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE)

suppressPackageStartupMessages({
  library(MazamaSpatialUtils)
  library(AirMonitor)
  library(AirMonitorPlots)
})

# Year will be passed in a as a paremter
###year = 2014

startdate <- sprintf("%d0701", year)
enddate <- sprintf("%d1101", year)
timezone <- "America/Los_Angeles"
```

```{r load_data}
# NOTE:  These paths are relative to the Rmd/ directory
airnow <- get(load(sprintf("../data/airnow_%d.rda", year)))
airsis <- get(load(sprintf("../data/airsis_%d.rda", year)))
wrcc <- get(load(sprintf("../data/wrcc_%d.rda", year)))

# NOTE:  We put airnow last so it's meta and data will be used  if an ID appears more than once
monitor <-
  monitor_combine(
    wrcc, airsis, airnow,
    replaceMeta = TRUE,
    overlapStrategy = "replace all"
  ) %>%
  monitor_dropEmpty() %>%
  monitor_trimDate()

```

# Air Quality Monitors in `r year`

_Disclaimer: Data presented here come from a variety of sources and do not 
represent official EPA measurements. Please visit
[AirNow](https://www.airnow.gov) for official measurements._

----

The Chelan-Douglas-Okanogan area had `r nrow(monitor$meta)` monitor-deployments 
during the `r year` July - October wildfire season. These includes both regulatory 
monitors that are part of the EPA AQS system as well as "temporary" monitors 
deployed by state and federal agencies during wildfires.

This page provides an overview of monitoring data available in the USFS AirFire 
archives. Additional monitoring data may be available from state and tribal
agencies.

Click on a dot in the map below to learn more about each monitor-deployment.

```{r airnow_map}
monitor %>%
  monitor_leaflet(
    extraVars = c(
      "deploymentType",
      "dataIngestSource",
      "AQSID"
    )
  )
```

## Hourly data

By plotting hourly measurements for all monitors at once, we can do a quick
visual QC of available data. Clusters of points 
around a very high value may signal problems with a monitor and would require 
additional investigation to identify the sensor and assess the quality of that data.

```{r airnow_timeseriesPlot}
monitor %>%
  monitor_timeseriesPlot(
    addAQI = TRUE
  )

monitorCount <- nrow(monitor$meta) * 1.5
```

## Daily averages

Here, we plot daily averages for all monitors with enough data for this 
calculation. Some temporary monitors may not have enough valid data points per
day and will be omitted from the plots below.

```{r airnow_dailyBarplot, fig.height = monitorCount}
gg <-
  ggplot_pm25Timeseries(
    monitor,
    startdate = startdate,
    enddate = enddate
  ) +
  ggtitle("Daily average PM2.5") +
  stat_dailyAQCategory(timezone = timezone) +
  facet_grid(rows = vars(locationName))

suppressWarnings({ print(gg) })

```

-----





