---
title: "Chelan-Douglas-Okanogan Monitoring Data"
output:
  html_document: 
    css: report_styles.css
---

Processed on `r paste(lubridate::now(),format(lubridate::now(), "%Z"))`.

----


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE)

suppressPackageStartupMessages({
  library(MazamaSpatialUtils)
  library(AirMonitor)
  library(AirMonitorPlots)
})

# Year will be passed in a as a paremter
###year = 2014

startdate <- sprintf("%d0701", year)
enddate <- sprintf("%d1101", year)
timezone <- "America/Los_Angeles"
```

```{r load_data}
# NOTE:  These paths are relative to the Rmd/ directory
airnow <- get(load(sprintf("../data/airnow_%d.rda", year)))
airsis <- get(load(sprintf("../data/airsis_%d.rda", year)))
wrcc <- get(load(sprintf("../data/wrcc_%d.rda", year)))
```

# AirNow monitors in `r year`

The Chelan-Douglas-Okanogan area had `r nrow(airnow$meta)` AirNow
monitor-deployments during the `r year` fire season. Click on a dot in the map
below to learn more about each deployment.

```{r airnow_map}
airnow %>%
  monitor_leaflet()
```

## AirNow hourly data

It is ueful to plot hourly measurements and do a simple "gut check" visual QC
before we start combining them into daily averages.

```{r airnow_timeseriesPlot}
airnow %>%
  monitor_timeseriesPlot(
    addAQI = TRUE
  )
```

## AirNow daily averages

```{r airnow_dailyBarplot, fig.height = 7}
gg <-
  ggplot_pm25Timeseries(
    airnow,
    startdate = startdate,
    enddate = enddate
  ) +
  ggtitle("Daily average PM2.5") +
  stat_dailyAQCategory(timezone = timezone) + 
  facet_grid(rows = vars(locationName))

suppressWarnings({ print(gg) })
```

# AIRSIS monitors in `r year`

There were `r nrow(airsis$meta)` AIRSIS
monitor-deployments during the `r year` fire season.

```{r airsis_map, eval = nrow(airsis$meta) > 0}
airsis %>%
  monitor_leaflet()  
```

 ```{r eval = nrow(airsis$meta) == 0} 
 knitr::asis_output("## No data avaiable") 
 ``` 

## AIRSIS hourly data

```{r airsis_timeseriesPlot, eval = nrow(airsis$meta) > 0}
airsis %>%
  monitor_timeseriesPlot(
    addAQI = TRUE
  )
```

 ```{r eval = nrow(airsis$meta) == 0} 
 knitr::asis_output("## No data avaiable") 
 ``` 

## AIRSIS daily averages

```{r airsis_dailyBarplot, fig.height = 7, eval = nrow(airsis$meta) > 0}
gg <-
  ggplot_pm25Timeseries(
    airsis,
    startdate = startdate,
    enddate = enddate
  ) +
  ggtitle("Daily average PM2.5") +
  stat_dailyAQCategory(timezone = timezone) + 
  facet_grid(rows = vars(locationName))

suppressWarnings({ print(gg) })
```

 ```{r eval = nrow(airsis$meta) == 0} 
 knitr::asis_output("## No data avaiable") 
 ``` 

# WRCC monitors in `r year`

There were `r nrow(wrcc$meta)` WRCC
monitor-deployments during the `r year` fire season.

```{r wrcc_map, eval = nrow(wrcc$meta) > 0}
wrcc %>%
  monitor_leaflet()
```

 ```{r eval = nrow(wrcc$meta) == 0} 
 knitr::asis_output("## No data avaiable") 
 ``` 

## WRCC hourly data

```{r wrcc_timeseriesPlot, eval = nrow(wrcc$meta) > 0}
wrcc %>%
  monitor_timeseriesPlot(
    addAQI = TRUE
  )
```

 ```{r eval = nrow(wrcc$meta) == 0} 
 knitr::asis_output("## No data avaiable") 
 ``` 

## WRCC daily averages

```{r wrcc_dailyBarplot, fig.height = 7, eval = nrow(wrcc$meta) > 0}
gg <-
  ggplot_pm25Timeseries(
    wrcc,
    startdate = startdate,
    enddate = enddate
  ) +
  ggtitle("Daily average PM2.5") +
  stat_dailyAQCategory(timezone = timezone) + 
  facet_grid(rows = vars(locationName))

suppressWarnings({ print(gg) })
```

 ```{r eval = nrow(wrcc$meta) == 0} 
 knitr::asis_output("## No data avaiable") 
 ``` 



