---
title: "Air Quality Category Tables"
output:
  html_document: 
    css: report_styles.css
---

Processed on `r paste(lubridate::now(),format(lubridate::now(), "%Z"))`.

----

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE)

suppressPackageStartupMessages({
  library(AirMonitor)
})

# stateCode, timezone and month will be passed in a as a parameters
if ( FALSE ) {
  stateCode <- "CA"
  month <- 11
}

# NOTE:  Here we load a small dataset just so we can obtain the best timezone
timezone <-
  airnow_loadLatest() %>%
  monitor_filter(deploymentType != "Temporary") %>%
  monitor_filter(stateCode == !!stateCode) %>%
  monitor_bestTimezone()

monthName <- 
  MazamaCoreUtils::parseDatetime(
    sprintf("2024%02d15", month), 
    timezone = timezone
  ) %>% 
  strftime("%B", tzone = timezone)

stateName <-
  MazamaSpatialUtils::US_stateCodeToName(stateCode)

```

_Disclaimer: Data presented here come from a variety of sources and do not 
represent official EPA measurements. Please visit
[AirNow](https://www.airnow.gov) for official measurements._

----

Cumulative exposure to smoke is an important public health metric. This report 
summarizes the cumulative number of days air quality monitors in `r stateName` 
spent in each AQI category during the the month of `r monthName`.

The tables below include only permanent monitors measuring PM~2.5~ and show 
cumulative exposure under existing NAAQS (National Ambient Air Quality
Standards) and under the 
[2024 revised standards for PM2.5](https://www.epa.gov/pm-pollution/final-reconsideration-national-ambient-air-quality-standards-particulate-matter-pm).

In the tables and plots below, 'Old' designates cumulative days calculated using 
the 2023 PM~2.5~ NAAQS while 'New' is calculated using the 2024 revised PM~2.5~ 
NAAQS. The impact of the NAAQS revision is quite clear.

```{r year_loop, results = "asis", fig.width = 10, fig.height = 3, fig.align = "left"}

cat(sprintf("\n\n## %s in %s\n", monthName, stateName))

for ( year in 2014:2023 ) {
  
  # Define the local time month
  startString <- sprintf("%d%02d01", year, month)
  startdate <- MazamaCoreUtils::parseDatetime(startString, timezone = timezone)
  enddate <- startdate + lubridate::ddays(40)
  lubridate::day(enddate) <- 1
  
  # ----- Assemble data --------------------------------------------------------
  
  # NOTE:  These paths are relative to the Rmd/ directory
  airnow <- get(load(sprintf("../data/airnow_%d.rda", year)))
  
  monitor <-
    airnow %>%
    monitor_filter(stateCode == !!stateCode) %>%
    # NOT:  monitor_dailyStatistic() requires a single timezone
    monitor_filter(timezone == !!timezone)
  
  if ( nrow(monitor$meta) == 0 ) {
    cat(sprintf("\n\n### %s %d -- %d monitors in AirFire data archive\n", monthName, year, nrow(monitor$meta)))
  } else {
    cat(sprintf("\n\n### %s %d -- %d permanent monitors\n", monthName, year, nrow(monitor$meta)))
  }
  
  # Continue only if there is data
  if ( !monitor_isEmpty(monitor) ) {
    
    monitor <-
      monitor %>%
      monitor_filterDate(startdate, enddate) %>%
      monitor_filter(deploymentType != "Temporary")
    
    # Continue only if there is data
    if ( !monitor_isEmpty(monitor) ) {
      
      result <- try({
        
        # Guarantee that all 
        
        # ----- Create table with rownames for printing ------------------------------
        
        oldAQCSummary <-
          monitor %>%
          monitor_dailyStatistic(
            FUN = mean,
            na.rm = TRUE,
            minHours = 18,
            dayBoundary = c("LST")
          ) %>%
          monitor_dropEmpty() %>%
          monitor_toAQCTable(
            NAAQS = "PM2.5",
            siteIdentifier = "deviceDeploymentID"
          ) %>%
          colSums()
        
        newAQCSummary <-
          monitor %>%
          monitor_dailyStatistic(
            FUN = mean,
            na.rm = TRUE,
            minHours = 18,
            dayBoundary = c("LST")
          ) %>%
          monitor_dropEmpty() %>%
          monitor_toAQCTable(
            NAAQS = "PM2.5_2024",
            siteIdentifier = "deviceDeploymentID"
          ) %>%
          colSums()
        
        dailyAQCTable <- 
          dplyr::bind_rows(oldAQCSummary, newAQCSummary) %>%
          as.data.frame()
        
        rownames(dailyAQCTable) <- c("Old", "New")
        
        # ----- Print table ----------------------------------------------------------
        
        print(knitr::kable(
          dailyAQCTable,
          format = "html", table.attr = "style='width:95%; font-size:1.5rem; margin: 20px 60px 0px 15px; line-height:2em'"
        ))
        
        # ----- Create barplot -------------------------------------------------------
        
        # Reorder so that the horizontal barplot ends up with Old on top 
        df_barplot <-
          dplyr::bind_rows(newAQCSummary, oldAQCSummary) %>%
          as.data.frame()
        
        rownames(df_barplot) <- c("New", "Old")
        
        par(mar = c(1,3,3,1) + 0.1)
        
        barplot(
          as.matrix(t(df_barplot)),
          col = c(US_AQI$colors_EPA, "gray90"),
          horiz = TRUE,
          las = 1,
          ylim = c(0, 1.5),
          width = 0.5,
          axes = FALSE
        )
        
        par(mar = c(5,4,4,2) + 0.1)
        
        # title("Title goes here")
        
        legend(
          "top",
          legend = c(US_AQI$names_eng, "Missing"),
          fill = c(US_AQI$colors_EPA, "gray90"),
          horiz = TRUE,
          cex = 0.8,
          bty = 'n'
        )
        
      }, silent = TRUE)
      
      if ( "try-error" %in% class(result) ) {
        
        cat(sprintf("\n`Processing error:  Unable to calculate tables.`\n"))
        
      }
      
    }
    
  }
  
}
```


