---
title: "Air Quality Category Tables"
output:
  html_document: 
    css: report_styles.css
---

Processed on `r paste(lubridate::now(),format(lubridate::now(), "%Z"))`.

----

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE)

suppressPackageStartupMessages({
  library(AirMonitor)
})

```

_Disclaimer: Data presented here come from a variety of sources and do not 
represent official EPA measurements. Please visit
[AirNow](https://www.airnow.gov) for official measurements._

----

Cumulative exposure to smoke is an important public health metric. This report 
summarizes the cumulative number of days US air quality monitors  
spent in each AQI category each year.

The tables below include only permanent monitors measuring PM~2.5~ and show 
cumulative exposure under existing NAAQS (National Ambient Air Quality
Standards) and under the 
[2024 revised standards for PM2.5](https://www.epa.gov/pm-pollution/final-reconsideration-national-ambient-air-quality-standards-particulate-matter-pm).

In the tables and plots below, 'Old' designates cumulative days calculated using 
the 2023 PM~2.5~ NAAQS while 'New' is calculated using the 2024 revised PM~2.5~ 
NAAQS. The impact of the NAAQS revision is quite clear.

```{r year_loop, results = "asis", fig.width = 10, fig.height = 3, fig.align = "left"}

cat(sprintf("\n\n## US annual\n"))

for ( year in 2014:2023 ) {
  
  # NOTE:  These paths are relative to the Rmd/ directory
  airnow <- 
    get(load(sprintf("../data/airnow_%d.rda", year))) %>%
    monitor_filter(deploymentType != "Temporary")
  
  cat(sprintf("\n\n### %d -- %d permanent monitors in AirFire data archive\n", year, nrow(airnow$meta)))
  
  oldAQCList <- list()
  newAQCList <- list()
  
  # ===== BEGIN timezone loop ==================================================
  for ( timezone in unique(airnow$meta$timezone) ) {
    
    startString <- sprintf("%d0101", year)
    startdate <- MazamaCoreUtils::parseDatetime(startString, timezone = timezone)
    enddate <- startdate + lubridate::dyears(1)
    
    monitor <-
      airnow %>%
      # NOTE:  monitor_dailyStatistic() requires a single timezone
      monitor_filter(timezone == !!timezone) %>%
      monitor_filterDate(startdate, enddate)
    
    if ( !monitor_isEmpty(monitor) ) {
      
      oldAQCList[[timezone]] <-
        monitor %>%
        monitor_dailyStatistic(
          FUN = mean,
          na.rm = TRUE,
          minHours = 18,
          dayBoundary = c("LST")
        ) %>%
        monitor_dropEmpty() %>%
        monitor_toAQCTable(
          NAAQS = "PM2.5",
          siteIdentifier = "deviceDeploymentID"
        ) %>%
        dplyr::as_tibble()
      
      newAQCList[[timezone]] <-
        monitor %>%
        monitor_dailyStatistic(
          FUN = mean,
          na.rm = TRUE,
          minHours = 18,
          dayBoundary = c("LST")
        ) %>%
        monitor_dropEmpty() %>%
        monitor_toAQCTable(
          NAAQS = "PM2.5_2024",
          siteIdentifier = "deviceDeploymentID"
        ) %>%
        dplyr::as_tibble()
      
    }
    
  }
  # ===== END timezone loop ====================================================
  
  # Annual summaries
  oldAQCSummary <-
    oldAQCList %>%
    dplyr::bind_rows() %>%
    colSums()
  
  newAQCSummary <-
    newAQCList %>%
    dplyr::bind_rows() %>%
    colSums()
  
  dailyAQCTable <- 
    dplyr::bind_rows(oldAQCSummary, newAQCSummary) %>%
    as.data.frame()
  
  rownames(dailyAQCTable) <- c("Old", "New")
  
  # ----- Print table ----------------------------------------------------------
  
  print(knitr::kable(
    dailyAQCTable,
    format = "html", table.attr = "style='width:95%; font-size:1.5rem; margin: 20px 60px 0px 15px; line-height:2em'"
  ))
  
  # ----- Create barplot -------------------------------------------------------
  
  # Reorder so that the horizontal barplot ends up with Old on top 
  df_barplot <-
    dplyr::bind_rows(newAQCSummary, oldAQCSummary) %>%
    as.data.frame()
  
  rownames(df_barplot) <- c("New", "Old")
  
  par(mar = c(1,3,3,1) + 0.1)
  
  barplot(
    as.matrix(t(df_barplot)),
    col = c(US_AQI$colors_EPA, "gray90"),
    horiz = TRUE,
    las = 1,
    ylim = c(0, 1.5),
    width = 0.5,
    axes = FALSE
  )
  
  par(mar = c(5,4,4,2) + 0.1)
  
  # title("Title goes here")
  
  legend(
    "top",
    legend = c(US_AQI$names_eng, "Missing"),
    fill = c(US_AQI$colors_EPA, "gray90"),
    horiz = TRUE,
    cex = 0.8,
    bty = 'n'
  )
  
}
# END year loop
```


